---
title: "06-Share all your analysis"
output:
  dcTemplate::dc_lesson_template:
    fig_width: 6
    fig_height: 6
    highlight: pygments
---


```{r knitr_init, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)

## Global options
options(max.print = "75")
opts_chunk$set(cache = TRUE,
               prompt = FALSE,
               tidy = TRUE,
               comment = "> #",
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 75)
```

## Optional
This section can be deemed optional and read but not practiced if you are not yet at a stage where you need to provide others access to your Docker image. Feel free to move on to [Lesson 07 Examples of Workflow incorporation](07-dockerfiles.html) or keep reading for interest!


Now that we have learned how to work with a dockerfile, we can send all our analysis to a collaborator. 
We will share an image that contains all the dependencies that we need to ran our analysis, the data and the analysis.

What is important to note, is that you are provided with a single private repository on Docker Hub with the free level of access, so consider any images pushed to be publicly available. Be careful with the data that you include in this image if you do not want it shared!!

We will build this image via a dockerfile. Let's start with the basic verse rocker image we used before. 
This time we want to have a specific R version (3.3.2), which the developers make possible by tagging the images with the version.
See all available tags for the `rocker/verse` image [here](https://hub.docker.com/r/rocker/verse/tags/). The version tag is very
useful when you want your analysis to be **reproducible**.

```
FROM rocker/verse:3.3.2
```

As part of our analysis, we will use the gapminder data. We will need to install this package into our docker image.
Let's modify our dockerfile to install this package. 

```
RUN R -e "install.packages('gapminder', repos = 'http://cran.us.r-project.org')"
```

Now we just need to write our analysis and add it to our dockerfile.

For this analysis, we will create a plot of life expectancy vs. gdp per capita. 

On a new R script let's write the following analysis. 

```{r}
library(ggplot2)
library(gapminder)

life_expentancy_plot <- ggplot(data = gapminder) + 
	geom_point(aes(x = lifeExp, y = gdpPercap, colour = continent)) 

```

We will save this r script as analysis.R and add it to our dockerfile.

```
ADD analysis.R /home/rstudio/
```

Now we can build the image and check that we have everything we want to share with our collaborator. 

```
docker build -t my-analysis .
```

Our analysis will appear on the list of images. 

```
docker images
```

Launch your new image and check you have everything you want to include:

```
docker run -dp 8787:8787 my-analysis
```

Great! our analysis script is there and gapminder is installed. 

Now we can push our analysis to dockerhub.

On dockerhub click on *Create Repository*.
Choose a name (e.g. gapminder_my_analysis) and a description for your repository and click *Create*.

Log into the Docker Hub from the command line
```{}
docker login --username=yourhubusername --email=youremail@company.com
```
just with your own user name and email that you used for the account.
Enter your password when prompted. 

Check the image ID using

```{}
docker images
```
and what you will see will be similar to
```{}
REPOSITORY                         TAG                 IMAGE ID            CREATED             SIZE
my-analysis                      latest              dc63d4790eaa        2 minutes ago       3.164 GB
```

and tag your image
```{}
docker tag dc63d4790eaa yourhubusername/gapminder_my_analysis:firsttry
```

Push your image to the repository you created
```{}
docker push yourhubusername/gapminder_my_analysis
```

Your image is now available for everyone to use.

Now your collaborator can download your image. 

Your collaborator should type the following on their command line:

```
docker pull yourhubusername/gapminder_my_analysis:firsttry
```

They now have the image of your analysis exactly as you wrote it.

Go to [Lesson 07 Incorporating into a workflow](07-Incorporating-into-a-workflow.html) or back to the [main page](http://ropenscilabs.github.io/r-docker-tutorial/).